\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.58in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{array}
\usepackage[colorlinks=true,urlcolor=hkustblue,linkcolor=hkustblue]{hyperref}

\definecolor{hkustblue}{HTML}{003C71}
\definecolor{textgray}{HTML}{2B2F33}
\definecolor{muted}{HTML}{5A626A}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\renewcommand{\arraystretch}{1.0}

\newlength{\datecol}
\setlength{\datecol}{1.15in}
\newlength{\bodycol}
\setlength{\bodycol}{\dimexpr\textwidth-\datecol-0.22in\relax}

\newcommand{\cvsection}[1]{%
  \vspace{0.52em}
  \begin{tabular}{@{}>{\raggedleft\arraybackslash\small}p{\datecol}@{\hspace{0.22in}}>{\arraybackslash}p{\bodycol}@{}}
    & {\large\bfseries #1}\\[-0.22em]
    & {\color{hkustblue}\rule{\bodycol}{0.45pt}}
  \end{tabular}\par\vspace{0.2em}
}

\newcommand{\cventry}[4]{%
  \begin{tabular}{@{}>{\raggedleft\arraybackslash\small}p{\datecol}@{\hspace{0.22in}}>{\arraybackslash}p{\bodycol}@{}}
    #1 &
    \begin{minipage}[t]{\bodycol}
    \textbf{#2}#3%
    \if\relax\detokenize{#4}\relax\else\par\emph{#4}\fi
    \end{minipage}
  \end{tabular}\par
}

\newcommand{\cvline}[2]{%
  \begin{tabular}{@{}>{\raggedleft\arraybackslash\small}p{\datecol}@{\hspace{0.22in}}>{\arraybackslash}p{\bodycol}@{}}
    #1 & \begin{minipage}[t]{\bodycol}#2\end{minipage}
  \end{tabular}\par
}

\newenvironment{cvitems}{%
  \begin{tabular}{@{}>{\raggedleft\arraybackslash\small}p{\datecol}@{\hspace{0.22in}}>{\arraybackslash}p{\bodycol}@{}}
  &
  \begin{minipage}[t]{\bodycol}
  \begin{itemize}
  \setlength{\itemsep}{0.02em}
  \setlength{\topsep}{0.04em}
  \setlength{\parsep}{0pt}
  \setlength{\leftmargin}{1.15em}
}{%
  \end{itemize}
  \end{minipage}
  \end{tabular}\par
}

\newcommand{\entrysep}{\vspace{0.16em}}

\begin{document}
\color{textgray}
\fontsize{8.8pt}{10.2pt}\selectfont

\begin{tabular}{@{}>{\arraybackslash}p{0.52\textwidth}@{\hfill}>{\raggedleft\arraybackslash}p{0.42\textwidth}@{}}
  {\LARGE\bfseries Chenyu Lu} &
  Hong Kong\\
  &
  \href{mailto:cluba@connect.ust.hk}{cluba@connect.ust.hk}\\
  &
  \href{https://dylanluchenyu.github.io}{dylanluchenyu.github.io}\\
  &
  GitHub: \href{https://github.com/dylanluchenyu}{dylanluchenyu}
\end{tabular}

\cvsection{Profile}
\cvline{}{HKUST Computer Science and Mathematics undergraduate interested in machine learning, reinforcement learning, and large language models. I am currently a research assistant with Prof. Nian Si and Prof. Qifeng Chen, connecting mathematical structure with practical research infrastructure.}

\cvsection{Education}
\cventry{Sep 2024 -- Jun 2028}{Bachelor of Science in Computer Science \& Mathematics}{, Hong Kong University of Science and Technology}{Hong Kong}
\begin{cvitems}
  \item CGA: 3.906 / 4.3; Major GPA: 4.028 / 4.3, calculated from graded COMP and MATH coursework.
  \item Cumulative credits earned: 69.0.
  \item Relevant coursework: Data Structures, Computer Organization, Algorithms, Operating Systems, Linear Algebra, Probability, Multivariable Calculus, Mathematical Analysis, Game Theory, Topology.
\end{cvitems}
\entrysep
\cventry{Jul 2026}{Exchange Student}{, HKUST Summer Study Abroad, Tallinn University}{Tallinn, Estonia}
\entrysep
\cventry{2026 -- 2027}{Student Member}{, The Hong Kong Institution of Engineers}{Hong Kong}

\cvsection{Publications}
\cvline{ICLR 2026}{\textbf{Co-author paper, ICLR 2026 (Oral).} \href{https://arxiv.org/abs/2509.15221}{arXiv}\\
\emph{ScaleCUA: Scaling Open-Source Computer Use Agents with Cross-Platform Data}\\
Zhaoyang Liu, Jingjing Xie, ..., \textbf{Chenyu Lu}, Yunxiang Mo, ..., Wenhai Wang.\\
\textcolor{muted}{Contribution: data pipeline and cross-platform workflow components in the open-source codebase.}}

\cvsection{Research Experience}
\cventry{Jul 2026 -- Present}{Research Assistant}{, Reinforcement Learning Theory, HKUST}{Hong Kong}
\begin{cvitems}
  \item Supervisor: Prof. Nian Si.
  \item Working on reinforcement learning theory and decision-making under uncertainty.
  \item Supporting ongoing research through mathematical modeling, literature study, and proof development.
\end{cvitems}
\entrysep
\cventry{Jul 2026 -- Present}{Research Assistant}{, Machine Learning / Computer-Use Agents, HKUST}{Hong Kong}
\begin{cvitems}
  \item Supervisor: Prof. Qifeng Chen.
  \item Continuing ML and computer-use-agent research, building on prior ScaleCUA experience.
  \item Connecting large-scale data preparation, evaluation workflows, and reliable agent research infrastructure.
\end{cvitems}
\entrysep
\cventry{Jun 2025 -- Aug 2025}{UROP Research Assistant}{, GUI Agent Project, HKUST}{Hong Kong}
\begin{cvitems}
  \item Supervisors: Prof. Qifeng Chen and Dr. Zhaoyang Liu.
  \item Performed large-scale data collection and preprocessing for GUI-agent research.
  \item Co-authored ScaleCUA, accepted to ICLR 2026 as an Oral paper.
  \item Contribution in ScaleCUA: data pipeline and cross-platform workflow components in the open-source codebase.
\end{cvitems}
\entrysep
\cventry{Sep 2025 -- Dec 2025}{UROP Research Assistant}{, Zeto Project, HKUST}{Hong Kong}
\begin{cvitems}
  \item Supervisors: Prof. Dimitris Papadopoulos and Dr. Jiajun Xin.
  \item Conducted comparative analysis of UTXO and account-based models for blockchain protocol research.
  \item Studied cryptographic foundations and their application to protocol validation.
  \item Assisted with research documentation, data sorting, and project coordination.
\end{cvitems}

\newpage
\cvsection{Projects}
\cventry{2025}{OpenGVLab / ScaleCUA Contribution}{, open-source computer-use-agent research infrastructure}{}
\begin{cvitems}
  \item Contribution in ScaleCUA: data pipeline and cross-platform workflow components in the open-source codebase.
  \item Project: \href{https://github.com/OpenGVLab/ScaleCUA}{github.com/OpenGVLab/ScaleCUA}.
\end{cvitems}
\entrysep
\cventry{2026}{Proof Preview}{, offline LaTeX proof viewer for studying math with Codex}{}
\begin{cvitems}
  \item Built a local HTML viewer with bundled KaTeX for offline mathematical proof preview.
  \item Added a command-line helper that lets Codex write the latest proof and print a file viewer link.
  \item Project: \href{https://github.com/dylanluchenyu/proof-preview}{github.com/dylanluchenyu/proof-preview}.
\end{cvitems}

\cvsection{Teaching Experience}
\cventry{Sep 2025 -- Dec 2025}{Undergraduate Teaching Assistant}{, COMP2711 Discrete Mathematics, HKUST}{Hong Kong}
\begin{cvitems}
  \item Provided academic guidance on core discrete mathematics concepts.
  \item Assisted with assignment arrangement and course support.
\end{cvitems}
\entrysep
\cventry{2026.03}{Undergraduate Teaching Assistant}{, COMP4900 Graduation Requirements, HKUST}{Hong Kong}
\begin{cvitems}
  \item Helped students understand graduation requirements.
  \item Assisted with seminar registration checks and course administration.
\end{cvitems}

\cvsection{Awards and Honors}
\cvline{May 2026}{Champion, 11th HKUST Undergraduate Mathematics Competition, Junior Division.}
\cvline{Apr 2025}{Champion, 10th HKUST Undergraduate Mathematics Competition, Junior Division.}
\cvline{Fall 2024}{Dean's List, HKUST.}
\cvline{Spring 2025}{Dean's List, HKUST.}
\cvline{Fall 2025}{Dean's List, HKUST.}
\cvline{Spring 2026}{Dean's List, HKUST.}
\cvline{2024--2025}{HKSAR Government Scholarship Fund - Talent Development Scholarship.}
\cvline{2025--2026}{University's Scholarship Scheme for Continuing Undergraduate Students.}
\cvline{Sep 2022}{First Prize, National High School Mathematics Olympiad (Preliminary), Chinese Mathematical Society.}
\cvline{}{Merit Award, 2nd Pi Day Challenge, Qiuzhen College, Tsinghua University.}
\cvline{Aug 2023}{Top 99\% National Ranking, Yau Shing-tung Math Test.}

\cvsection{Skills}
\cvline{}{Programming: Python, C/C++, JavaScript.}
\cvline{}{Research areas: Machine learning, reinforcement learning theory, large language models.}
\cvline{}{Languages: Mandarin Chinese (native), English (proficient).}

\end{document}
